---
title: \vspace{6cm} \LARGE <center><strong> PFC Benefit and Budget Impact Calculator </strong></center>
date: <center><strong> `r format(Sys.Date(), '%d %B %Y')` </strong></center>
geometry: "left = 1cm, right = 1cm, top = 1.8cm, bottom = 2.5cm"
output:
  pdf_document:
    toc_depth: 5
    number_sections: true
    df_print: paged
params:
  country_name: NA
  scenario_type: NA
  dbase_path: NA
---


\centering
\raggedright
\newpage
\tableofcontents

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, 
                      message = F,
                      echo = F, 
                      eval = T,
                      dpi = 180, fig.width = 11, fig.height = 7, 
                      comment = " ")

## --- Define country and scenario
# country <- "Russia"
#scenario_run <- "FLS_Basecase"

scenario_run <- params$scenario_type
country <- params$country_name
active.dr <- params$dbase_path
# model scenarios -
# "FLS_Basecase"                      
# "FLS_Identification_100"            
# "FLS_Treatment_initiation_one_month"
# "FLS_Monitoring_100"                
# "FLS_Alendronate_only"              
# "FLS_Injectables_only"              
# "FLS_Injectables_only.max_reduction"
# "FLS_Adherence_100"                 
# "FLS_Perfect_FLS"                   
# "FLS_Hips_and_spines_only"          
# "FLS_Hips_only"


```

```{r load-packages}
# Install and load packages
if (!require(pacman)) install.packages("pacman")

pacman::p_load(
  tidyverse, ggeasy, here, kableExtra,
  data.table, scales, ggthemes, ggpubr,
  googlesheets4, pander, RColorBrewer, patchwork, 
  readxl, DBI, RSQLite, data.table
)

# Define the default theme for all plots
theme_set(theme_hc(base_size = 15))

# generate subtitle for inputs
input_title <- str_replace_all(params$scenario_type, 
                             pattern = "_", 
                             replacement = " ") # use scenario name and remove underscores to create subtitle

```


\
\
\


\newpage


---
author: "Country: `r country`"
---


```{r my-functions}
# 1. Function to transform a dataframe (pivot_longer, then pivot wider)
# mostly the tables from the PFC model outputs

df_transform <- function(d_frame, 
                         names_col = "metric"){
 #takes a table and double-transforms it 
d_frame %>% 
  pivot_longer(cols = -1, names_to = {{names_col}}, 
               values_to = "vals") %>% 
  pivot_wider(names_from = 1, 
              values_from = 3)
}

# 2. Function to help print nice numeric output
nice_numOut <- function(dframe){
  dframe %>% 
    mutate_if(is.numeric, ~ comma(.)) %>% 
    mutate_at(vars(ncol(dframe)), ~ sub("\\.\\d+$", "", .)) # just to make sure
                                                            # last column has no decimal points
}

# Function to list fields and get data
CollectGsheetData_rmd <- function(connection = "Genericcountry",
                              table_name = "FLS_Basecase",
                              na.rm.value = TRUE){
  # # store scenario name on the global enviroment
  # scenarioName <<- table_name
  
  
  
  # create a connection
  tbl_conn <- dbConnect(SQLite(),
                             paste0(active.dr,"/inputs_databases/",connection, ".db"))
  # glance at the data
  if(na.rm.value == TRUE){
    tbl(tbl_conn, table_name) %>% filter(!is.na(Value))
  } else {
    tbl(tbl_conn, table_name)
  }

}

```


```{r inputs-reading, message=FALSE}
#------------------------------------------------------------------------------------------------------------------
# generic data reading based on country above

model.inputs_SQL <- CollectGsheetData_rmd(connection = str_replace(country, # define connection
                                              pattern = " ",
                                              replacement = ""),
                  table_name = scenario_run,
                  na.rm.value = FALSE) %>%
  collect() %>% tibble::rowid_to_column(var = "row.index")

# identify rows that have all NAs
miss_rows_SQL <- model.inputs_SQL %>% 
  filter_at(vars(c(Input,name, Description, Value)),
            all_vars(is.na(.)))

# remove the all NA rows and also rows after "Risk of Mortality"
after.risk.rows <- c(599:753)

model.inputs_SQL <- model.inputs_SQL[-c(miss_rows_SQL$row.index), ] %>% select(-1) %>% as_tibble()

# -- Reading costs inputs

# cost_country <- paste(country, "costs")
# 
# 
# costs.inputs<-  read_sheet("https://docs.google.com/spreadsheets/d/1CA4y892IxzgU2S9Z5qbqBt-aG8dULt8B6uQIjQGAN-U/edit?usp=sharing",
#                            sheet= cost_country,
#                            range = "A1:E304",
#                            col_types= "c") %>% tibble::rowid_to_column(var = "row.index")

costs.inputs <- CollectGsheetData_rmd(connection = str_replace(country, # define connection
                                              pattern = " ",
                                              replacement = ""),
                  table_name = scenario_run,
                  na.rm.value = FALSE) %>%
  collect() %>% filter(category == "Cost values") %>% 
  tibble::rowid_to_column(var = "row.index") %>% select(-category)

# # identify rows that have all NAs
# miss_rowsCosts <- costs.inputs %>% 
#   filter_at(vars(c(Input,name, Description, Value)),
#             all_vars(is.na(.)))

costs.inputs <- costs.inputs %>% select(-c(1, 3)) %>% as_tibble()

# rows to style
cost_rows <- costs.inputs %>% tibble::rowid_to_column(var = "row.index") %>% filter(is.na(Description)) %>% pull(row.index)

# ---------------------------------------------------------------------------------
# Reading general inputs (applicable to all countries)

# general.inputs<-  read_sheet("https://docs.google.com/spreadsheets/d/1CA4y892IxzgU2S9Z5qbqBt-aG8dULt8B6uQIjQGAN-U/edit?usp=sharing",
#                            sheet= "General",
#                            range="A14:D49",
#                            col_types= "c") %>% select("Input"=1, "Name"=3, "Value"=4) 

general.inputs <- CollectGsheetData_rmd(connection = str_replace(country, # define connection
                                              pattern = " ",
                                              replacement = ""),
                  table_name = scenario_run,
                  na.rm.value = FALSE) %>%
  collect() %>% filter(category == "Time lag effects") %>% select("Input"=1, "Name"=3, "Value"=4) 
```


```{r}
# reading the descrisption names
# model_descrp <- read_excel(here("report", 
#                                 "Summary.Reports",
#                                 "mode_inputs_descriptions.xlsx")) %>% 
#   select(Name, full_name) %>% na.omit()


model_descrp <- CollectGsheetData_rmd(connection = "inputs_descriptions",
                  table_name = "inputs_descriptions",
                  na.rm.value = FALSE) %>% collect()


model.inputs_SQL_new <- model.inputs_SQL %>% 
  left_join(model_descrp, 
            by = c("name" = "Name")) %>% 
  select(Input, full_name, Value, Source) %>% 
  slice(1:752) %>% 
  mutate(
    Source = replace(Source, which(full_name %in% c("Mean average age of men with a hip fracture",
                                                    "Mean average age of women with a hip fracture")), "") # ONLY for Russia
  )

row_ids_SQL <- model.inputs_SQL_new %>% tibble::rowid_to_column(var = "row.index") %>% filter(is.na(full_name)) %>% pull(row.index)


```


```{r, message=FALSE}
# # tired refracture risk group (combine with model inputs)
# # using SQL database
# tiered_grp_SQL <- CollectGsheetData_rmd(connection = str_replace(country, # define connection
#                                               pattern = " ",
#                                               replacement = ""),
#                   table_name = scenario_run,
#                   na.rm.value = FALSE) %>%
#   collect() %>% tibble::rowid_to_column(var = "row.index") %>% 
#   slice(600:607) %>% select(-row.index) %>% 
#   select("Input" = 1, "full_name" = 2, Value = 4, "Source" = 5) 

```

---
subtitle: "`r paste(input_title, "Model Inputs Report", sep = " - ")`"
---


```{r}
# Preparing data for various chapters/table of contents
content_1 <- model.inputs_SQL_new %>% 
  slice(1:11) %>% bind_rows(
    model.inputs_SQL %>% slice(751:757) %>% 
  select(Input, full_name = 3, Value, Source)
  ) %>% 
  mutate(
    Value = replace(Value, which(is.na(Input) & is.na(full_name)), NA_character_),
    Input = replace(Input, which(is.na(Input) & is.na(full_name)), "Cohort sizes")
  )



```


# \hspace{7cm} Clinical and epidemiological inputs

## Epidemiology of fractures
```{r}
# # always include the tiered fracture risk
# use.risk.profiles <-  1
# 
# if (use.risk.profiles == 0){
#   model.inputs_SQL_new %>% select(Input, Name = full_name, Value, Source) %>%
#   replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
#   kable(longtable = T) %>% kable_paper("hover") %>%
#   kable_styling(bootstrap_options = c("striped", "scale_down"),
#                 font_size = 13, position = "left") %>%
#   row_spec(row = 0, font_size = 16, bold = T) %>%
#   row_spec(row = row_ids_SQL, italic = T,
#            background = "#e7e7b1", font_size = 14, bold = T)
# } else {
# bind_rows(
#     model.inputs_SQL_new,
#     #tiered_grp_SQL
#   ) 

# model.inputs_SQL_new %>% select(Input, Name = full_name, Value, Source) %>%
#   replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
#   kable(longtable = T) %>% 
#   kable_styling(latex_options = c("scale_down", "repeat_header"),
#                 font_size = 11, position = "left",
#                 repeat_header_text = "") %>%
#   row_spec(row = 0, font_size = 13, bold = T) %>%
#   row_spec(row = c(row_ids_SQL), italic = T,
#            background = "#e7e7b1", font_size = 12, bold = T) %>% 
#     column_spec(c(1,2), width = "12em") %>% 
#     column_spec(3, width = "5em") %>% 
#     column_spec(4, width = "20em")
# }

content_1 %>%
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = c(1,12), italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage

## Risk of re-fractures

```{r}
# highlight rows (1)
model.inputs_SQL_new %>% 
  slice(12:48) %>%
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Treatment practice
```{r}
# 
model.inputs_SQL_new %>% 
  slice(49:181) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```
\newpage

## Medication
### Medications after 1y of romo
```{r}
model.inputs_SQL_new %>% 
  slice(182:215) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```
\newpage

### Medications after 2y of abaloparatide
```{r}
model.inputs_SQL_new %>% 
  slice(216:248) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```
\newpage

### Medications after 2y of teriparatide
```{r}
model.inputs_SQL_new %>% 
  slice(249:281) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage

## Probability of being identified
```{r}
model.inputs_SQL_new %>% 
  slice(282:288) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Time to treatment onset
```{r}
model.inputs_SQL_new %>% 
  slice(289:295) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Effect of medications on risk of subsequent fracture
```{r}
model.inputs_SQL_new %>% 
  slice(296:326) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Primary adherence
```{r}
model.inputs_SQL_new %>% 
  slice(327:447) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Monitoring
```{r}
model.inputs_SQL_new %>% 
  slice(448:472) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Adherence
```{r}
model.inputs_SQL_new %>% 
  slice(473:549) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Annual decline in adherence (between months 25 and 60)
```{r}
model.inputs_SQL_new %>% 
  slice(550:578) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Risk of mortality

```{r}
model.inputs_SQL_new %>% 
  slice(579:598) %>% 
  rename(Name = full_name) %>% 
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T) %>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

<!-- \newpage -->

<!-- ## Tiered re-fracture risk -->
<!-- ```{r} -->
<!-- model.inputs_SQL_new %>%  -->
<!--   slice(599:715) %>%  -->
<!--   rename(Name = full_name) %>%  -->
<!--   replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>% -->
<!--   kable(longtable = T) %>%  -->
<!--   kable_styling(latex_options = c("scale_down", "repeat_header"), -->
<!--                 font_size = 11, position = "left", -->
<!--                 repeat_header_text = "") %>% -->
<!--   row_spec(row = 0, font_size = 13, bold = T) %>% -->
<!--   row_spec(row = 1, italic = T, -->
<!--            background = "#e7e7b1", font_size = 12, bold = T) %>%  -->
<!--     column_spec(c(1,2), width = "12em") %>%  -->
<!--     column_spec(3, width = "5em") %>%  -->
<!--     column_spec(4, width = "20em") -->
<!-- ``` -->

<!-- \newpage -->

<!-- ## Treatment rate by risk tier -->
<!-- ```{r} -->
<!-- model.inputs_SQL_new %>%  -->
<!--   slice(716:752) %>%  -->
<!--   rename(Name = full_name) %>%  -->
<!--   replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>% -->
<!--   kable(longtable = T) %>%  -->
<!--   kable_styling(latex_options = c("scale_down", "repeat_header"), -->
<!--                 font_size = 11, position = "left", -->
<!--                 repeat_header_text = "") %>% -->
<!--   row_spec(row = 0, font_size = 13, bold = T) %>% -->
<!--   row_spec(row = 1, italic = T, -->
<!--            background = "#e7e7b1", font_size = 12, bold = T) %>%  -->
<!--     column_spec(c(1,2), width = "12em") %>%  -->
<!--     column_spec(3, width = "5em") %>%  -->
<!--     column_spec(4, width = "20em") -->
<!-- ``` -->


\newpage

# \hspace{7cm} Resource use and cost inputs

```{r}
# rows to exclude
exclude <- c(200:206,207:215, 216:222, 254:258)

cost_rows <- c(1,2,6,15,19,27,29,33,38,40,41,94,147,200,231,247,251,264,271)

# costs.inputs %>%
#   slice(-exclude) %>% view()
#   select(Input, Name = Description, Value, Source) %>%
#   replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
#   kable(longtable = T) %>% 
#   kable_styling(latex_options = c("scale_down", "repeat_header"),
#                 font_size = 11, position = "left",
#                 repeat_header_text = "") %>%
#   row_spec(row = 0, font_size = 13, bold = T) %>%
#   row_spec(row = cost_rows, italic = T,
#            background = "#e7e7b1", font_size = 12, bold = T)%>% 
#     column_spec(c(1,2), width = "12em") %>% 
#     column_spec(3, width = "5em") %>% 
#     column_spec(4, width = "20em")
```

## Treatment following fracture

```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(2:26) %>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = c(1,5,8,14,18), italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Hospital length of stay (for those admitted)

```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(19:26) %>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Number of community consultations for spine fractures not seen in hospital
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(27:28)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Hospital costs - Generic
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(29:32)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Hospital costs - Site specific
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(33:37)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Community care costs
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(38:39)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Average time spent by stage
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(41:199)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = c(1, 54, 107), italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage
## Medication yearly costs
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(200:230)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Discharge destination by fracture site
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(231:246)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```


\newpage
## Temporary rehab- average length of stay
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(247:250)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```



\newpage
## Destination after temporary rehab
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(251:263)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage
## Average number of clinic (outpatient) vists following..

```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(264:270)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage
## Costs after discharge
```{r}
costs.inputs %>% 
  slice(-exclude) %>% 
  slice(271:275)%>% 
    select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```



\newpage

## Staff costs 
```{r}
costs.inputs %>% 
  slice(200:206) %>% 
  add_row(.after = 0) %>% 
  mutate(
    Input = replace(Input, which(is.na(Value)&is.na(Description)), "Staff cost"),
    Input = replace(Input, which(Input == "Staff costs"), "")
  ) %>% 
  select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## Laboratory tests
```{r}
costs.inputs %>% 
  slice(207:215) %>%
  add_row(.after = 0) %>% 
  mutate(
    Input = replace(Input, which(is.na(Value)&is.na(Description)), "Proportions"),
    Input = replace(Input, which(Input == "Laboratory tests - proportions"), NA_character_)
  ) %>%
  add_row(.after = 7) %>% 
  mutate(
    Input = replace(Input, which(is.na(Value)&is.na(Input)), "Costs"),
    Input = replace(Input, which(Input == "Laboratory tests - costs"), NA_character_)
  ) %>% 
  select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = c(1,8), italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```

\newpage

## DXA scans
```{r}
costs.inputs %>% 
  slice(216:222)%>%
  add_row(.after = 0) %>% 
  mutate(
    Input = replace(Input, which(is.na(Value)&is.na(Description)), "Proportions"),
    Input = replace(Input, which(Input == "DXA- proportions"), NA_character_)
  ) %>%
  add_row(.after = 7) %>% 
  mutate(
    Input = replace(Input, which(is.na(Value)&is.na(Input)), "Costs"),
    Input = replace(Input, which(Input == "DXA - cost"), NA_character_)
  )  %>% 
  select(Input, Name = Description, Value, Source) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "", Source = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = c(1,8), italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(c(1,2), width = "12em") %>% 
    column_spec(3, width = "5em") %>% 
    column_spec(4, width = "20em")
```



\newpage

# \hspace{7cm} General (non country-specific) inputs

```{r}
general.inputs %>% 
  add_row(.after = 0) %>%
   mutate(
    Input = replace(Input, which(is.na(Value)&is.na(Name)), "Medications")
  ) %>%
  replace_na(replace = list(Input = "", Name = "", Value = "")) %>%
  kable(longtable = T) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"),
                font_size = 11, position = "left",
                repeat_header_text = "") %>%
  row_spec(row = 0, font_size = 13, bold = T) %>%
  row_spec(row = 1, italic = T,
           background = "#e7e7b1", font_size = 12, bold = T)%>% 
    column_spec(1, width = "15em") %>% 
    column_spec(2, width = "28em") %>% 
  column_spec(3, width = "5em") 
```
















