---
title: "NeoBAC Weekly Report"
output:
  html_document:
    df_print: paged
  pdf_document: default
params:
  start_date_rmd: NA
  end_date_rmd: NA
always_allow_html: true

---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(data.table)
library(here)
library(pander)
library(janitor)
library(knitr)



```


```{r}
start_date <- params$start_date_rmd %>% as.Date()
end_date <- params$end_date_rmd %>% as.Date()

## test Dates
#start_date <- "2020-06-21" %>% as.Date()
#end_date <- Sys.Date() %>% as.Date()

#setorder(mydates, -dates)


```

# All  Neobac 

## Demographic characteristics

```{r}
setDT(final_demoTable) 

final_demoTable <- final_demoTable[metric != "Age (days) - Mean±SD" ]
kable(final_demoTable)
```

## Distribution of age

```{r, fig.width=9, fig.height=5, dpi=1000}


age <- neobac_ids_report[age_days >=0] 
xbrks_age <- seq(from = 0, to = 30, by = 5)
age[, age_days := as.factor(age_days)]
ggplot(data = age, aes(age_days))+
  labs(title = "Distribution of age", x = "Age (days)", y = "Frequency")+
  geom_bar()+
  theme_hc()
  #scale_x_continuous(breaks = xbrks_age )
```
\newpage


## Study Flow diagram

```{r,  out.width='100%', dpi = 1000}
 # saved graph as png in current working directory
overall_chart_path <- paste0(mwd, "/overall_chart.png")
knitr::include_graphics(overall_chart_path)
```



## Summary of all admission blood  cultures taken

```{r}

blood_culture_report[, .(freq = .N), by = .(site, bac_positive)] %>%
  pivot_wider(names_from = site, values_from = freq ) %>%
  adorn_totals(where = c("col", "row")) %>%
  pander()
```


## Number Collected before and After Antibiotics

```{r}

blood_culture_report[, .(freq = .N), by = .(site, receive_antibio_adm_b4_bld)] %>%
   pivot_wider(names_from = receive_antibio_adm_b4_bld, values_from = freq ) %>%
  adorn_totals(where = c("col", "row")) %>%
  pander()
```


## Contamination rate

```{r, fig.width=8, fig.height=5, dpi=600}
y_brks = seq(from = 0, to = max(tab1$Perc), by = 5)
gg_conta_rate <- ggplot(tab1, aes(date_collect, Perc, color = site)) +
  theme_hc()+
  geom_line(size = 1) +
  labs(y = "Percentage", x = "Month", title =  "Blood cultures contamination rate per site")+
  scale_x_date(date_labels = "%b-%y", date_breaks = "1 month")+
  scale_y_continuous(breaks = y_brks)+
  scale_color_hc()
  # geom_text(aes(date_collect, Perc,label = Perc), position = position_dodge(width = 15),
  #           vjust = 0.05, hjust = 0.5)

gg_conta_rate
```


\newpage

## All Organisms Identified

```{r}
ast_org <- merge(blood_culture_report[, .(pk_specimen_id, site)],
                  ast_report, by = "pk_specimen_id")


ast_org_all <- ast_org[, .(serial_study_id, site,  pk_isolate,
                         pk_specimen_id, species_full_name, type)]

ast_org_all_sum <- ast_org_all[, .(Number_isolates = .N),
                                 by = .(type, species_full_name)]

setorder(ast_org_all_sum, -type, -Number_isolates)

kable(ast_org_all_sum)
```


\newpage

## AST Results 

```{r}
tab_antibiotics <- AST_sm[, .(freq = .N), 
                          by = .(site, species_full_name, drug_tested, resistance_result) ] %>%
  pivot_wider(names_from = resistance_result, 
              values_from = freq) %>% setDT()

tab_antibiotics[["NA"]] = NULL
nms_anti <- c("R", "S", "I")
tab_antibiotics[, (nms_anti) := lapply(.SD, function(x) ifelse(is.na(x), 0, x)), .SDcols = nms_anti]
tab_antibiotics[, sum_all := Reduce(`+`, .SD), .SDcols = nms_anti]
tab_antibiotics <- tab_antibiotics[sum_all > 0]
tab_antibiotics[, sum_all := NULL]
anti_id <- c("site", "species_full_name", "drug_tested")
tab_antibiotics_m <- melt(tab_antibiotics, id.vars = anti_id,
                          variable.name = c("resisistance"))

tab_antibiotics_m1 <- tab_antibiotics_m %>%
  pivot_wider(names_from = drug_tested, values_from = value)

ast_path <- paste0(mwd, "/lab_datasets/ast_resistance.csv")
setorder(tab_antibiotics_m1 ,species_full_name )
write.csv(tab_antibiotics_m1,
          file = ast_path, row.names = F,
          na = "")

#pander(tab_antibiotics)
```

## AST Plots


```{r, fig.width=8, fig.height=5, dpi = 600}

library(viridis)
tab_ast_list <- split(tab_antibiotics_m ,
                      f = list( tab_antibiotics_m$species_full_name))

cond <- lapply(tab_ast_list, function(x) nrow(x) > 0) %>%
  unlist()

tab_ast_list <- tab_ast_list[cond]

plot_list1 <- list()
for (i in 1:length(tab_ast_list)) {
  this = tab_ast_list[[i]]
  nm = this[, unique(species_full_name)]
  plot_list1[[i]] <-  ggplot(this, aes(drug_tested, value, fill = resisistance))+
    geom_bar(stat = "identity") +
    facet_wrap(~site, ncol = 1, scales = "free_y")+
    scale_fill_viridis_d()+
    labs(title = nm)+
    theme_plot()+
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
}

plot_list1

```

# NeoBAC report for dates `r start_date` to `r end_date`

## Blood culture collected 


```{r}
bld_week <- blood_culture_report[between(date_collect, start_date, end_date)]
bld_week[, .(freq = .N), by = .(site, bac_positive)] %>%
  pivot_wider(names_from = site, values_from = freq ) %>%
  adorn_totals(where = c("col", "row")) %>%
  pander()
```

## Number Collected before and After Antibiotics

```{r}

bld_week[, .(freq = .N), by = .(site, receive_antibio_adm_b4_bld)] %>%
   pivot_wider(names_from = receive_antibio_adm_b4_bld, values_from = freq ) %>%
  adorn_totals(where = c("col", "row")) %>%
  pander()
```



## Organisms 

```{r}
ast_week <- merge(bld_week[, .(pk_specimen_id, site)],
                  ast_report, by = "pk_specimen_id")


ast_week_all <- ast_week[, .(serial_study_id, site,  pk_isolate,
                         pk_specimen_id, species_full_name, type)]

ast_week_all_sum <- ast_week_all[, .(Number_isolates = .N),
                                 by = .(type, species_full_name)]

setorder(ast_week_all_sum, -type, -Number_isolates)
kable(ast_week_all)
```

## AST results all results

- Download table from NeoBAC App

```{r, eval=FALSE, include=FALSE}
2+2
# ast_pthogens <- ast_week[type == "Pathogen"] %>% 
#   select(serial_study_id, pk_isolate,
#          pk_specimen_id, species_full_name, esbl, contains("s_"))
# 
# kable(ast_pthogens)

```

